PM Mungbean meta-analysis

### 2020-06-22 02_Preliminary_analysis.Rmd
Add labels to graphs, Markdown syntax edits

```{r yield_vol}
# Outputs the table and graph
source("R/yield_volatility.r") # function to investigate the volatility in yields
# Volatility is the range between the upper and lower 97.5 and 2.5 % quartiles
YV1 <-
   yield_volatility(genotype_by_trial = FALSE, control_only = FALSE)
YV1[[2]] + 
   scale_fill_usq()
YV1[[3]]
```

@@

In crop rain could be a significant factor which contributes to the end of season grain yield.
To investigate this effect I will use a linear model (GY ~ SR) where seasonal rainfall represents a specific time frame with respect to planting time.
Multiple time frames were tested from 20 days prior to planting, to 100 days after planting.

>>>>

```{r yield_vol}
# Outputs the table and graph
source("R/yield_volatility.r") # function to investigate the volatility in yields
# Volatility is the range between the upper and lower 97.5 and 2.5 % quartiles
YV1 <-
   yield_volatility(genotype_by_trial = FALSE, control_only = FALSE)
YV1[[2]] + 
   scale_fill_usq()
V1[[3]]
```

@@

In0-crop rain could be a significant factor which contributes to the end of season grain yield.
To investigate this effect I will use a linear model (GY ~ SR) where seasonal rainfall represents a specific time frame with respect to planting time.
Multiple time frames were tested from 20 days prior to planting, to 100 days after planting.
